Risk Perceptions for Wearable Devices

### 2015-04-15 tex-inputs/methodology.tex
killed an orphan

\subsection{Motivation}
In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.

@@

\subsubsection{Technology Risk Perceptions}
Fischhoff \etal performed a seminal study of the perceived risks surrounding 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for these technologies. They told participants to think about all people affected by the technology, and to think about long-term versus short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10). We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing and how these technologies compared to more familiar technologies.
%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

>>>>

\subsection{Related Work}
In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.

@@

\subsubsection{Technology Risk Perceptions}
Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}. Participants were asked to separately think of the risks then benefits, considering all people affected, long-term effects, and short term effects. Then, the participants respectively rated these technologies on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10). We apply their methodology to evaluate perceived risks and benefits of technologies related to wearable computing with respect to more familiar technologies.
%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
